### 2012-12-23 inst/examples/allee.Rmd
example allee model, against estimated with correct structure

```{r set-options, echo = FALSE, cache = FALSE, external = TRUE, include = FALSE}
opts_chunk$set(external = TRUE, cache = FALSE, cache.path = "myers-cache/")
read_chunk('gaussian-process-control.R')
library(knitcitations)
```

@@

```{r Ricker}
```

We use the Ricker model

```{r sdp-pars-ricker}
sigma_g <- 0.05
z_g <- function(sigma_g) rlnorm(1, 0, sigma_g) #1+(2*runif(1, 0,  1)-1)*sigma_g #
x_grid <- seq(0, 2.5 * K, length=101)
h_grid <- x_grid
profit = function(x,h) pmin(x, h)
delta <- 0.01
OptTime = 20
reward = profit(x_grid[length(x_grid)], x_grid[length(x_grid)]) + 1 / (1 - delta) ^ OptTime 
xT <- 0
```

with parameters `r p`.

@@

```{r sim-obs}
```

@@

```{r lag-data}
```

@@

```{r par-est-BH}
```

Estimate data under the BH model

```{r gp-fit, dependson="lag-data"}
```

@@

>>>>

```{r set-options, echo = FALSE, cache = FALSE, external = TRUE, include = FALSE}
opts_chunk$set(external = TRUE, cache = FALSE, cache.path = "allee-cache/", warning=FALSE)
read_chunk('gaussian-process-control.R')
library(knitcitations)
```

@@

```{r RickerAllee}
```

We use the model of Allen

```{r sdp-pars}
```

With parameters `r p`.

@@

```{r sim-with-harvest}
```

@@

@@

```{r MLE-RickerAllee}
```

```{r gp-priors}
```

```{r gp-fit}
```

@@

```{r gp-posteriors}
```
